---
# Change this file's ending from .Rmd to .qmd for this to work.
title: Long title
title_short: title
subtitle: Subtitle
institute: "Institute of Medical Biometry\\linebreak University of Heidelberg"
author: "Long author\\linebreak author@imbi.uni-heidelberg.de"
author_short: author
date: Date
format: 
  beamer:
    template: markdown_beamer_template.tex
    keep-tex: true
    cite-method: natbib
linestretch: 1.1
header-includes:
    - \input{imbi_layout_markdownbeamer_en.tex}
bibliography: bibliography.bib
biblio-title: "References"
classoption: "aspectratio=169"
# Uncomment the following to two lines and insert the output path
# knit: (function(inputFile, encoding) {
#  rmarkdown::render(inputFile, encoding = "UTF-8", output_dir = "Put/output/path/here",  output_file = paste0("STUDYTITLE_report_", Sys.Date()) )})
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
    echo = FALSE
)
```

```{r dependencies, include=FALSE}
library(tidyverse)
```

### Content
\tableofcontents

# Section 1
## Subsection 1
### Frame title
The appearance of the title slide can be adjusted in
imbi_layout_markdownbeamer_en.tex (e.g. no subtitle).
\vspace{1cm}

You can define which header level to use for frames with the `slide_level`
parameter in the YAML header.
By default, the highest header level followed by content defines frames. 
Higher header levels define sections.  
See https://bookdown.org/yihui/rmarkdown/beamer-presentation.html for other
details.

# Section 2

---

Three horizontal bars create a frame without title.
Declare new commands like $\Var$ at the end of imbi_layout_markdownbeamer_en.tex.

* This
* is
* a
* list

### Here comes a big plot


```{r plot}
#| fig.height: 4
#| fig.width: 8
#| fig.align: 'center'
#| echo: FALSE
#| message: FALSE
#| results:  'hide'
#| out-width:  95%
#| out-height:  95%
par(mar = c(5, 5, 0.5, 2))
plot(mtcars$mpg, mtcars$disp)
```

---

### Here comes a scaled down plot
\small
The chunk options `fig.height` and `fig.width` determine the settings of the
R graphics device. This influences e.g. the relative size of axis labels
in comparison to the plot. It works similarly to when you adjust the size of the
plot window in the bottom right corner of Rstudio.

`out-width` and `out-height` determine the size of the figure that is included
into the latex document. They are passed as arguments to the latex function
`\includegraphics`. Essentially, they determine how the plot is scaled.

```{r plotsmall}
#| fig.height: 4
#| fig.width: 8
#| fig.align: 'center'
#| echo: FALSE
#| message: FALSE
#| results:  'hide'
#| out-width:  45%
#| out-height:  45%
par(mar = c(5, 5, 0.5, 2))
plot(mtcars$mpg, mtcars$disp)
```

---


References of all cited sources are created automatically at the end when
bilbiography file is given in the YAML header [@ref].
